A generalized definition of multidimensional item response theory parameters

### 2024-07-09 output/paper_draft/paper_M2PLM_parameters.Rmd
Adds formulas for computing coordinates (WiP)
Adds derivation of item coordinates

The aforementioned properties are easier to apprehend with
a visual representation of the items.
The most appropriate way of representing them graphically is
a vector plot [@ackerman_creating_1994].
This kind of plot allows representing several items altogether and analyze them
in terms of their multidimensional parameters [@ackerman_graphical_1996]:
An item vector will be applied at a direction and (signed) distance
from the origin of the coordinate system given by its $`r MIL_PARAM`$ parameter
and will have a length equal to its $`r MDISC_SYM`$ parameter.
Its direction will also be given by the direction component of $`r MIL_PARAM`$,
so its orientation will always pass through the origin.
On the basis of these conditions, we will need to compute
the origin and end coordinates of the vector,
denoted by $`r ORIGIN_ITEM_BASIS`$ and $`r END_ITEM_BASIS`$, respectively.

In an orthogonal basis it is easy to compute the coordinates,
as they are simply the orthogonal projections on the respective axes.
In the oblique case it is not so simple though, but we take advantage of the
orthornormalization introduced above.
In $`r TEST_SPACE_STD_BASIS`$ , the origin and end coordinates are
$`r ORIGIN_ITEM_ORTH`$ and $`r END_ITEM_ORTH`$, respectively,
and they correspond to the coordinates in $`r TEST_SPACE_BASIS`$ transformed
according to Equation \@ref(eq:discr-vector-std),
i.e., $`r ORIGIN_ORTH_EQ`$ and $`r END_ORTH_EQ`$.
Given the mapping of $`r TEST_SPACE_STD_BASIS`$ basis onto $`r LS_ORTH_BASIS`$,
Equation \@ref(eq:dir-cos-vec-std) gives
the direction cosines in $`r TEST_SPACE_STD_BASIS`$.
For the origin coordinates we have that

>>>>

The aforementioned properties are easier to apprehend with
a visual representation of the items.
The most appropriate way of representing them graphically is
a vector plot [@ackerman_creating_1994].
This kind of plot allows representing several items altogether and analyze them
in terms of their multidimensional parameters [@ackerman_graphical_1996]:
An item vector will be applied at a direction and (signed) distance
from the origin of the coordinate system given by its $`r MIL_PARAM`$ parameter
and will have a length equal to its $`r MDISC_SYM`$ parameter.
Its direction will also be given by the direction component of $`r MIL_PARAM`$,
so its orientation will always pass through the origin.
On the basis of these conditions, we need to compute
the origin and end coordinates of the vector,
denoted by $`r ORIGIN_ITEM_BASIS`$ and $`r END_ITEM_BASIS`$, respectively.

In an orthogonal basis it is easy to compute the coordinates,
as they are simply the orthogonal projections onto the corresponding axis.
In the oblique case it is not so simple though, but we take advantage of the
orthornormalization introduced above.
In basis $`r TEST_SPACE_STD_BASIS`$, the origin and end coordinates are
$`r ORIGIN_ITEM_ORTH`$ and $`r END_ITEM_ORTH`$, respectively,
and they correspond to the coordinates in $`r TEST_SPACE_BASIS`$ transformed
according to Equation \@ref(eq:discr-vector-std),
i.e., $`r ORIGIN_TRANSF_EQ`$ and $`r END_TRANSF_EQ`$.
Given the mapping of $`r TEST_SPACE_STD_BASIS`$ onto $`r LS_ORTH_BASIS`$,
the direction cosines in $`r TEST_SPACE_STD_BASIS`$
are $`r DIR_COS_ITEM_VEC_STD`$.
Therefore,

\begin{align}
  `r ORIGIN_ORTH_EQ` \\
  `r END_ORTH_EQ`.
\end{align}

Applying Equation \@ref(eq:dir-cos-vec-std),
for the origin coordinates we have that

\begin{equation}
  `r ORIGIN_ORTH_DISCR_EQ`                              (\#eq:origin-orth-discr)
\end{equation}

which, operating, results in

\begin{align}
  `r ORIGIN_ITEM_COORDS_EQ`    \\
  `r ORIGIN_TRANSF_SQUARED_EQ` \\
  `r ORIGIN_INNERPROD_EQ`      \\
  `r ORIGIN_INNERPROD_DIAG_EQ`;
\end{align}

\begin{equation}
  `r ORIGIN_INNERPROD_DIR_COS_EQ`.                   (\#eq:origin-coords-result)
\end{equation}

The end coordinates can be computed by a similar procedure, which results in

\begin{equation}
  `r END_ITEM_COORDS_EQ`.                               (\#eq:end-coords-result)
\end{equation}
